Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2019-11-13 paper2_JNLS/paper.tex
NM

@@

@@

\subsection{Sampling from the Gibbs measures}

\nick{Include a short description of the sampling method}

\begin{equation}
\mean{Q} = \frac{\int Q \exp\left(-\theta \Ham \right) d\mu}{ \int \exp\left(-\theta \Ham \right) d\mu}
\approx \frac{\sumsamp Q_i \exp(-\theta \Ham_i)} {\sumsamp \exp(-\theta \Ham_i)}
\end{equation}

>>>>

\nick{Edit this}
To compute the transfer function, we use a weighted random sampling strategy, with samples drawn from the uniform distribution ($d\mu$ or $\Gz$, which notation?) and the weight provided by the Gibbs form \eqref{Gibbs}.
\begin{equation}
\mean{Q} = \frac{\int Q \exp\left(-\theta \Ham \right) d\mu}{ \int \exp\left(-\theta \Ham \right) d\mu}
\approx \frac{\sumsamp Q_i \exp(-\theta \Ham_i)} {\sumsamp \exp(-\theta \Ham_i)}
\end{equation}
For computing the transfer function, this simple, weighted averaging approach is preferable to more sophisticated MCMC because it allows you to collect a large number of samples once, and then simply change the weights for different $\theta$. MCMC would require to completely restart the sampling for each individual $\theta$.

@@

\nick{We should simply comment that we use MHMC to initialize the direct simulations.}

@@
